---
title: "Final_Project"
output: html_document
date: "2023-04-20"
---

Variables to look at: 
Heart rate variability, resting heart rate, amount of sleep, energy burned from previous day, skin temp
sleep efficiency (intercept)


Narrowing it down to semi-easily observable characteristics that we think will be influential and people can implement to better their own sleep

```{r}
data_w = na.omit(read.csv("Sleep_Cycles.csv"))

head(data_w)

summary(data_w)

plot(data_w$Asleep.duration..min.)

data_w_sub = data_w[,c("Resting.heart.rate..bpm.","Heart.rate.variability..ms.","Energy.burned..cal.","Skin.temp..celsius.","Asleep.duration..min.","Sleep.efficiency..")]
```

```{r}
sleep_lm = lm(Sleep.efficiency.. ~ ., data=data_w_sub)

summary(sleep_lm)

full_int_data = data_w[,-c(1:3,13,14)]

full_sleep_lm  = lm(Sleep.efficiency.. ~.,data=full_int_data)

summary(full_sleep_lm)
```
```{r}
lm_2 = lm(Sleep.efficiency.. ~ Recovery.score..+Resting.heart.rate..bpm.+Heart.rate.variability..ms.+Sleep.need..min., data=data_w)
summary(lm_2)

efficiency_pred=predict(lm_2,newdata=data_2)
mean_squared_Error =mean((data_2$Sleep.efficiency..-efficiency_pred)^2)
r_squared=cor(data_2$Sleep.efficiency..,efficiency_pred)^2

r_squared

```


```{r}
data_2 = na.omit(read.csv("Sleep_Cycles_2.csv"))

head(data_2)

data_2_sub = data_2[,c("Resting.heart.rate..bpm.","Heart.rate.variability..ms.","Energy.burned..cal.","Skin.temp..celsius.","Asleep.duration..min.","Sleep.efficiency..")]

sleep_lm_2 = lm(Sleep.efficiency.. ~ ., data=data_2_sub)

summary(sleep_lm_2)
```



Determining which factors of sleep most influences sleep performance 

Hypothesis: Energy burned from the previous day would be most influential 





